Evaluating infectious disease forecasts with allocation scoring rules

### 2023-05-24 alloscore_manuscript/allocation.tex
Added a bit to paragraph 1, as well as some notes for other citations I will add in -BWR

Infectious disease forecasts have been used to inform decision-making about a wide variety of measures designed to reduce disease spread and/or mitigate the severity of disease outcomes. Such decision-making applications include the allocation of limited medical supplies such as ventilators \citep{bertsimas2021predictionsCOVID}, implementation of social distancing measures such as stay-at-home policies, planning site selection for vaccine trials \citep{bertsimas2021predictionsCOVID}, and strategies for public health communication campaigns.

>>>>

% People using infectious disease forecasting as an input to decision making:

%Center for Forecasting and Outbreak Analytics (CDC) https://www.cdc.gov/forecast-outbreak-analytics/annual-report/2023/key-accomplishments.html#omicron-response anual report
%  Bertsimas gives data-driven approach to provide clincal insights and support ventilator allocation for policy makers,

% "Our results have been used at the clinical level by several hospitals to triage patients, guide care management, plan ICU capacity, and re-distribute ventilators. At the policy level, they are currently supporting safe back-to-work policies at a major institution and vaccine trial location planning at Janssen Pharmaceuticals, and have been integrated into the US Center for Disease Control’s pandemic forecast."

%Grohskopf "Prevention and Control of Seasonal Influenza with Vaccines: Recommendations of the Advisory Committee on Immunization Practices — United States, 2022–23 Influenza Season" - Current CDC recommendations state that "Timing, intensity, and severity of the 2022-23 influenze season cannot be predicted"

% Rainisch G, Shankar M, Wellman M, Merlin T, Meltzer MI. Regional spread of Ebola virus, West Africa, 2014. Emerg Infect Dis 2015;21:444–7 Forecast of geographic spread of Ebola which helped aid decision-makers in allocation of surveillance resources.

% MI Meltzer - Estimating the Future Number of Cases in the Ebola (example of Ebola prediction informing policy to increase ERU capacities among other measures)

%https://www.cdc.gov/mmwr/preview/mmwrhtml/su6303a1.htm

Infectious disease forecasting models have emerged as important tools in public health decision making. Predictions of disease dynamics have been used to inform decision-making about a wide variety of measures designed to reduce disease spread and/or mitigate the severity of disease outcomes. In a simple example, estimates of expected onset of flu season have been used to inform national vaccination strategies  \cite{igboh2023timing}, and forecasts of ebola dynamics have been used to allocate surveillance resources \cite{meltzer2014estimating}. Other examples of past decision making applications of infectious disease forecasts include the allocation of limited medical supplies such as ventilators \cite{bertsimas2021predictionsCOVID}, implementation of social distancing measures such as stay-at-home policies, planning site selection for vaccine trials \cite{bertsimas2021predictionsCOVID}, and strategies for public health communication campaigns.

For example, estimates of expected onset of flu have been used to inform national flu vaccination strategies \cite{igboh2023timing}, and allocation of ebola surveillance resources \cite{meltzer2014estimating}.  Other past decision making applications of infectious disease forecasts include the allocation of limited medical supplies such as ventilators \cite{bertsimas2021predictionsCOVID}, implementation of social distancing measures such as stay-at-home policies, planning site selection for vaccine trials \cite{bertsimas2021predictionsCOVID}, and strategies for public health communication campaigns.
